Serum Biomarkers of Nutrition Pre and Post CFTR Modulator Use in Children with Cystic Fibrosis

### 2022-04-18 Edith Zemanick/CF Nutrition/cf_nutrition.Rmd
groups of visits within 3 months of each other

```{r}
# Vitamins
vit = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report Vitamins_throughDecember2021.xlsx")
vit = vit %>% select(`Patient ID`,Date,VitaminA_Retinol:`Vitamin E Gamma`)
# New age at start
mods = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report CFTR Modulators_throughDecember2021.xlsx")
mods = mods[mods$Modulator %in% c('Kalydeco','Trikafta'),]
mods = mods %>% select(`Patient ID`,Modulator,`Earliest Date in Registry`) %>% 
  pivot_wider(id_cols = `Patient ID`,names_from = Modulator,
              values_from = `Earliest Date in Registry`)
colnames(mods)[2:ncol(mods)] = paste0(colnames(mods)[2:ncol(mods)]," Date")
mods$`First Mod Date` = pmin(mods$`Trikafta Date`,mods$`Kalydeco Date`,na.rm = T)
mods$`Second Mod Date` = pmax(mods$`Trikafta Date`,mods$`Kalydeco Date`)
# Add pancreatic status
pancreatic = read_excel("./CF Info/Sweat Tests from Internal Database_genotype class_withPancStatus.xlsx")
pancreatic = pancreatic %>% rename(`Patient ID` = PatientID) %>% select(`Patient ID`,PancreaticStatus)
# FEV1 and BMI
fev = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report_PFTs_ThroughDecember2021.xlsx")
fev = fev %>% select(PatientID,Date,BMI,`FEV1 % pred`) %>% rename(`Patient ID` = PatientID)
# Merge
df = full_join(vit,fev,by = c("Patient ID", "Date")) %>% filter(`Patient ID` %in% mods$`Patient ID`)
df = left_join(df,mods,by = "Patient ID")
df = left_join(df,pancreatic,by = "Patient ID")
```

>>>>

```{r}
# Vitamins
vit = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report Vitamins_throughDecember2021.xlsx")
vit = vit %>% select(`Patient ID`,Date,VitaminA_Retinol:`Vitamin E Gamma`)
# New age at start
mods = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report CFTR Modulators_throughDecember2021.xlsx")
mods = mods[mods$Modulator %in% c('Kalydeco','Trikafta'),]
mods = mods %>% select(`Patient ID`,Modulator,`Earliest Date in Registry`) %>% 
  pivot_wider(id_cols = `Patient ID`,names_from = Modulator,
              values_from = `Earliest Date in Registry`)
colnames(mods)[2:ncol(mods)] = paste0(colnames(mods)[2:ncol(mods)]," Date")
mods$`First Mod Date` = pmin(mods$`Trikafta Date`,mods$`Kalydeco Date`,na.rm = T)
mods$`Second Mod Date` = pmax(mods$`Trikafta Date`,mods$`Kalydeco Date`)
# Add pancreatic status
pancreatic = read_excel("./CF Info/Sweat Tests from Internal Database_genotype class_withPancStatus.xlsx")
pancreatic = pancreatic %>% rename(`Patient ID` = PatientID) %>% select(`Patient ID`,PancreaticStatus)
# FEV1 and BMI
fev = read_excel("./Edith Zemanick/CF Nutrition/Data_Raw/Report_PFTs_ThroughDecember2021.xlsx")
fev = fev %>% select(PatientID,Date,BMI,`FEV1 % pred`) %>% rename(`Patient ID` = PatientID)
# Merge
df = full_join(vit,fev,by = c("Patient ID", "Date")) %>% filter(`Patient ID` %in% mods$`Patient ID`)
df = left_join(df,mods,by = "Patient ID")
df = left_join(df,pancreatic,by = "Patient ID")
# Match close dates 
df_list = split.data.frame(df,df$`Patient ID`)
t = df_list[[1]]
lapply(df_list, function(d){
  d = d %>% arrange(Date)
  # Calculate difference between all dates (in seconds)
  dis = as.matrix(dist(d$Date))
  # Which within 3 months
  pairs = as.data.frame(which(dis <= 24*60*60*90 & lower.tri(dis),arr.ind = T))
  # Groups
  group = NA
  length(group) = nrow(pairs)
  g = 1
  for (i in 1:length(group)) {
    if (i == 1){
      group[i] = 1 
      next
    } else {
      k = j
      j = as.numeric(pairs[i,])
      if(length(intersect(j,k)) == 0){
        g = g + 1
      }
      group[i] = g
    }
  }
  pairs$group = group
  # Add to d
  d$group = seq(from = max(pairs$group)+1,by = 1,length.out = nrow(d))
  d$group[pairs$row] = pairs$group
})
```
